---
title: "Lab 5"
author: "Group Member Names - here"
output:
  pdf_document: default
---

```{r, include = F}
library(dplyr)
library(readr)
library(knitr)
set.seed(10212019)
```


## Lab Overview
All students attending class in the group can turn in a single document with each participants name. Students not attending class will need to complete their own lab.

Download the movies earnings dataset. In today's lab, we are interested in using the budget of a film to estimate the earnings.


```{r}
movies <- read_csv('http://math.montana.edu/ahoegh/teaching/stat446/movies_earnings.csv')
movies
```


#### 1. (5 points)
Before looking at the data, summarize the relationship you expect between the budget of the film and the earnings.

#### 2. (5 points)
A SRS of 100 movies has been taken for you from the dataset. Create a plot of earnings vs. budget for these movies. How does this figure match your expectations?

```{r}
movies_sample <- movies %>% sample_n(100)
```


#### 3. (5 points)
Report a point estimate of the population ratio $B$. Where does this show up on the graphic you created for problem 1?

#### 4. (5 points)
Assume that you know the population mean for the movie budget,
```{r}
xbar_U <- movies %>% summarize(mean(budget)) %>% pull()
```

using the 100 samples, calculate the mean earnings per film with both the SRS estimator and the ratio estimator.

#### 5. (5 points)

Discuss which esimator from part 4 you prefer.